Synthesis of Linear Functional Programs

### 2021-05-09 article/article.tex
typo

\mypara{Program Synthesis from Polymorfic Refinement Types} The
work~\cite{DBLP:conf/pldi/PolikarpovaKS16} also studies synthesis
recursive functional programs but in a more ``advanced'' setting. The
specification is a combination of two rich forms of types: polymorphic and
refinement types (which correspond to a first-order logic through the
Curry-Howard isomorphism) -- this is an interesting combination that offers
``expressive power and decidability, which enables automatic
verification--and hence synthesis--of nontrivial programs''.  Their
approach to refinement types consists a new algorithm that supports
decomposition of the refinement specification, allowing for separation
between the language of specification and programs and making the
approach amenable to compositional synthesis techniques.

>>>>

\mypara{Program Synthesis from Polymorphic Refinement Types} The
work~\cite{DBLP:conf/pldi/PolikarpovaKS16} also studies synthesis
recursive functional programs but in a more ``advanced'' setting. The
specification is a combination of two rich forms of types: polymorphic and
refinement types (which correspond to a first-order logic through the
Curry-Howard isomorphism) -- this is an interesting combination that offers
``expressive power and decidability, which enables automatic
verification--and hence synthesis--of nontrivial programs''.  Their
approach to refinement types consists a new algorithm that supports
decomposition of the refinement specification, allowing for separation
between the language of specification and programs and making the
approach amenable to compositional synthesis techniques.
